Oracle Bone Inscription Recognition\\ with CNN and Template Matching

### 2019-12-17 2-oracle/report/paper.tex
submission update for 2-oracle

\documentclass[journal]{IEEEtran}

@@

\begin{figure}[h]
	\centering
	\begin{minipage}{\linewidth}
		\subfigure[Confusion Matrix for 10 Category Classification]{
			\includegraphics[width=\linewidth]{fig/confusion_oraclenet_conv10.png}
			\label{fig:network-confusion-10}
		}
	\end{minipage}
	\begin{minipage}{\linewidth}
		\hspace{-2em}
		\subfigure[Confusion Matrix for 40 Category Classification]{
			\includegraphics[width=1.15\linewidth]{fig/confusion_oraclenet_conv40.png}
			\label{fig:network-confusion-40}
		}
	\end{minipage}
	\caption{Validation Results}
	\label{fig:network-confusion}
\end{figure}

@@

\subsection{Evaluation and Improvements}
To recognize characters in the test set, we need to first preprocess the samples.

>>>>

\documentclass[journal,conference]{IEEEtran}

@@

\begin{figure}[h]
	\centering
	\begin{minipage}{\linewidth}
		\hspace{-1.5em}
		\subfigure[Confusion Matrix for 10 Category Classification]{
			\includegraphics[width=1.1\linewidth]{fig/confusion_oraclenet_conv10.png}
			\label{fig:network-confusion-10}
		}
	\end{minipage}
	\begin{minipage}{\linewidth}
		\hspace{-2em}
		\subfigure[Confusion Matrix for 40 Category Classification]{
			\includegraphics[width=1.15\linewidth]{fig/confusion_oraclenet_conv40.png}
			\label{fig:network-confusion-40}
		}
	\end{minipage}
	\caption{Validation Results}
	\label{fig:network-confusion}
\end{figure}

@@

\subsection{Model Evaluation}
To recognize characters in the test set, we need to first preprocess the samples.
